---
title: "Data Gathering and Analysis"
author: "Guohao Chen"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Data Gathering and Analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r}
library(tuber)
library(tidyverse)
library(lubridate)
library(stringi)
library(wordcloud)
library(gridExtra)
library(httr)
library(purrr)
library(tibble)
library(magrittr)
library(jsonlite)
library(tidyr)
library(plotly)
```

# Link to YouTube API will require OAuth: Credentials and Secret 

```{r, eval=FALSE, auth}
yt_oauth("278404634406-0t19licmr7cm01gh5v5tn68l5cu26vu6.apps.googleusercontent.com", "FImGFkYTB18S2d3GO9Y8iypg")
```

# Get Video Ids from a Channel - Dataset 1

```{r, eval=FALSE}
#Get Videos from the New York Times by putting in channel_id that can be found on the YouTube channel html
#Only look at the videos published after 2016
videos = yt_search(term="",type="video", channel_id = "UCqnbDFdCpuN8CMEg0VuEBqA")
videos = videos %>%
  mutate(date = as.Date(publishedAt)) %>%
  filter(date > "2016-01-01") %>%
  arrange(date)
saveRDS(videos, file = "videos.rds")

```

# Dataset 1 : ID, published date, video title & etc.


```{r}
#Display the first dataset gathered, this does not include important performance and engagement data including number of view, comments, like, dislike. 
Videos <- readRDS(file = "videos.rdS")
head(Videos)

```

```{r}
summary(Videos)

```

# Get performance data : Dataset 2
## Function: get_single_video_stats

```{r}
#Get more specifc viedeo performance data for a simple video by its video ID : viewCount, likeCount & etc. 
get_single_video_stats <- function(x)
{get_stats(video_id = x)}

```

```{r,eval= FALSE}
#Test on a single video by the video ID
get_single_video_stats ("SwBA1qb5ENg")
```

$`id`
[1] "SwBA1qb5ENg"

$viewCount
[1] "59753"

$likeCount
[1] "343"

$dislikeCount
[1] "16"

$favoriteCount
[1] "0"

$commentCount
[1] "45"


## Get Dataset 2 : Video ID with viewCount, likeCount, commentCount & etc.

```{r,eval=FALSE}
#Get more specifc video data for all the videos gathered before by their video_ID
videodata <- lapply(as.character(videos$video_id), get_single_video_stats)
saveRDS(videodata, file = "videodata.rds")
```

```{r}
videodata <- readRDS(file = "videodata.rds")
head(videodata)
```

## Transform Dataset 2
```{r}
#Transform dataset2 from nested list to a matrix
videodata1 <- do.call(rbind,videodata)
head(videodata1)
```

```{r}
#Transform dataset2 to a dataframe and unlist nested list in each column
videodata2 <- data.frame(videodata1)
videodata2$id <- unlist (videodata2$id)
videodata2$viewCount <- unlist (videodata2$viewCount)
videodata2$likeCount <- unlist (videodata2$likeCount)
videodata2$dislikeCount <- unlist (videodata2$dislikeCount)
videodata2$favoriteCount <- unlist (videodata2$favoriteCount)
videodata2$commentCount <- unlist (videodata2$commentCount)
head(videodata2)
```

```{r}
#Unifify video_id column names in the two datasets
colnames(videodata2)[1] <- "video_id"
```

```{r}
#Select relavant columns in dataset1

videos2 <- Videos[,c("video_id", "title", "publishedAt","date", "thumbnails.default.url","description")]
head(videos2)
```

# Join dataset 1 & 2
```{r}
#Join two datasets together by video_id
NYT_Video<- dplyr::full_join(videos2, videodata2, by = "video_id")
head(NYT_Video)
```


# Clean the combined dataset
```{r}
#Change all xCount columns from character to Numeric
  NYT_Video$viewCount <-as.numeric(NYT_Video$viewCount)
  NYT_Video$likeCount <-as.numeric(NYT_Video$likeCount)
  NYT_Video$dislikeCount <-as.numeric(NYT_Video$dislikeCount)
  NYT_Video$commentCount <-as.numeric(NYT_Video$commentCount)
  
head(NYT_Video)
```


```{r}
summary(NYT_Video)

```

# Visualize relationship between view with number of like, dislike, and commment
```{r}

library(ggplot2)
library(gridExtra)
library(grid)
p1 = ggplot(data = NYT_Video) + geom_point(aes(x = viewCount, y = likeCount))
p2 = ggplot(data = NYT_Video) + geom_point(aes(x = viewCount, y = dislikeCount))
p3 = ggplot(data = NYT_Video) + geom_point(aes(x = viewCount, y = commentCount))
grid.arrange(p1, p2, p3, ncol = 2)
```

# Print Linear Relationships between performance metrics
```{r}
# Print Linear Relationships between performance metrics
Like_View <- lm(NYT_Video$likeCount~NYT_Video$viewCount)
Dislike_View <- lm(NYT_Video$dislikeCount~NYT_Video$viewCount)
Comment_View <- lm(NYT_Video$commentCount~NYT_Video$viewCount)
Comment_Like <- lm(NYT_Video$commentCount~NYT_Video$likeCount)
Comment_Dislike <- lm(NYT_Video$commentCount~NYT_Video$dislikeCount)
print(Like_View)
print(Dislike_View)
print(Comment_View)
print(Comment_Like)
print(Comment_Dislike)


```
### Insight1: People are much more likely to comment when they dislike a video rather than comment a video when they like it
### Insight2: 1/100 of people view the video will click 'like'.


# Get Average Length of video titles : 64 characters.

```{r}
library(stringr)
VideoTitle <- NYT_Video$title
titlelength <- str_length(VideoTitle)
mean(titlelength)
```

# Provide a summary for videos in different 
## Clean "Title" Column
```{r}
#The title of the video includes several parts with "|" as seperator.
#Seperate the title to different parts 
library(tidyr)
NYT_Video <- separate(data = NYT_Video, col = title, into = c("part1", "part2", "part3", "part4"), sep = "\\|")
```

```{r}
head(NYT_Video)
```

#Get the average performance metrics by different categories
```{r}
NYT_Video_Summary <- NYT_Video %>%
  group_by(part2) %>%
  summarize(number=n(), mean_viewCount = mean(viewCount, na.rm = TRUE), mean_likeCount = mean(likeCount, na.rm = TRUE), mean_dislikeCount = mean(dislikeCount, na.rm = TRUE),mean_commentCount = mean(commentCount, na.rm = TRUE))
head(NYT_Video_Summary)
```


```{r}
summary(NYT_Video_Summary)

```

```{r}
# The Part 2 that indicates the category of the video is very messy due to the summary. 
# This requires data cleaning using stringr package.
NYT_Video_Summary <- NYT_Video_Summary %>%
  arrange(desc(number))
top_n(NYT_Video_Summary,10)
```

#Clean Part2/Category data
```{r}
NYT_Video$part2 <- str_replace_all(NYT_Video$part2, "NYT - Opinion", "NYT Opinion")
```

```{r}
NYT_Video %>%
  filter(str_detect(part2, "Opinion"))
```

```{r, eval=FALSE}
NYT_Video$part2 <- str_replace_all(NYT_Video$part2, "NYT Op-Docs", "Op-Docs")
NYT_Video$part2 <- str_replace_all(NYT_Video$part2,  "Op-Docs", "NYT Op-Docs")
NYT_Video %>%
  filter(str_detect(part2, "Op-Docs"))
```

```{r}
NYT_Video$part2 <- str_replace_all(NYT_Video$part2, "NYT - Dispatches	", "NYT Dispatches")
NYT_Video$part2 <- str_replace_all(NYT_Video$part2, "NYT Dispatches", "Dispatches")
NYT_Video$part2 <- str_replace_all(NYT_Video$part2,  "Dispatches", "NYT Dispatches")
NYT_Video %>%
  filter(str_detect(part2, "Dispatches"))
```

```{r, eval=FALSE}
NYT_Video$part2 <- str_replace_all(NYT_Video$part2, "NYT - Visual Investigations", "NYT Visual Investigations")
NYT_Video$part2 <- str_replace_all(NYT_Video$part2, "NYT Visual Investigations", "Visual Investigations")
NYT_Video$part2 <- str_replace_all(NYT_Video$part2, "Visual Investigations", "NYT Visual Investigations")
NYT_Video %>%
  filter(str_detect(part2, "Investigations"))
```

```{r, eval=FALSE}
NYT_Video$part2 <- str_replace_all(NYT_Video$part2, "Times Documentaries", "Times Documentary")
NYT_Video %>%
  filter(str_detect(part2, "Docu"))
```

```{r, eval=FALSE}
NYT_Video$part2 <- str_replace_all(NYT_Video$part2, "The New York Times", "NYT")
NYT_Video %>%
  filter(str_detect(part2, "NYT"))
```

```{r, eval=FALSE}
NYT_Video$part2 <- str_replace_all(NYT_Video$part2, "Diary of a Song", "NYT - Diary of a Song")
NYT_Video %>%
  filter(str_detect(part2, "Diary"))
```

```{r, eval=FALSE}
NYT_Video$part2 <- str_replace_all(NYT_Video$part2, "NYT - Out There", "Out There")
NYT_Video %>%
  filter(str_detect(part2, "Out"))
```

```{r, eval=FALSE}
NYT_Video$part2 <- str_replace_all(NYT_Video$part2, "Conception Season 2", "NYT - Conception")
NYT_Video %>%
  filter(str_detect(part2, "NYT - Conception"))
```

```{r, eval=FALSE}
NYT_Video$part2 <- str_replace_all(NYT_Video$part2, "NYT - NYT - Diary of a Song", "NYT - Diary of a Song")
NYT_Video$part2 <- str_replace_all(NYT_Video$part2, "NYT - NYT Dispatches", "NYT Dispatches")

```


#Show Cleaned Category Summary Data

```{r}
NYT_Video_Summary <- NYT_Video %>%
  group_by(part2) %>%
  summarize(number=n(), mean_viewCount = mean(viewCount, na.rm = TRUE), mean_likeCount = mean(likeCount, na.rm = TRUE), mean_dislikeCount = mean(dislikeCount, na.rm = TRUE),mean_commentCount = mean(commentCount, na.rm = TRUE))
NYT_Video_Summary %>%
  arrange(desc(number))
   
```

```{r, eval=FALSE}
save(NYT_Video_Summary, file= "summary.rds")
```

```{r, eval=FALSE}
save(NYT_Video, file= "joined_datasets.rds")
```


##Visulized Top View, Dislike & Comment Sections
```{r, warning=FALSE}
library(plotly)
m <- list(
  l = 50,
  r = 50,
  b = 100,
  t = 100,
  pad = 4
)

NYT_Video_Summary %>% 
  arrange(desc(mean_viewCount)) %>%
      head(6) %>%
         plot_ly(x = ~part2, y = ~mean_viewCount, type = 'bar') %>%
            add_trace(y = ~part2)  %>%
          layout(title="Top View Sections", autosize = F, width = 800, height = 500, margin= m)

##Top Dislike Sections
NYT_Video_Summary %>% 
  arrange(desc(mean_dislikeCount)) %>%
      head(6) %>%
         plot_ly(x = ~part2, y = ~mean_dislikeCount, type = 'bar') %>%
            add_trace(y = ~part2)  %>%
  layout(title="Top Dislike Sections", autosize = F, width = 800, height = 500)

##Top Comment Sections
NYT_Video_Summary %>% 
  arrange(desc(mean_commentCount)) %>%
      head(6) %>%
         plot_ly(x = ~part2, y = ~mean_commentCount, type = 'bar') %>%
            add_trace(y = ~part2)  %>%
    layout(title="Top Comment Sections", autosize = F, width = 800, height = 500)

#blockspace for plot
#blockspace for plot
#blockspace for plot
#blockspace for plot
#blockspace for plot
#blockspace for plot
#blockspace for plot
#blockspace for plot
#blockspace for plot
#blockspace for plot


```




```{r}
# Get Section Data 
visual_Investigations <- NYT_Video %>% filter(str_detect(part2, "Visual Investigations"))
```

```{r}
#Get Section Data
NYTOpinion <- NYT_Video %>% filter(str_detect(part2, "Opinion"))
```

## Visulize Daily Average Views to show NYT Video Channel Performance

```{r}
Performance <- NYT_Video %>%
  group_by(date) %>%
   summarise(maxview = max(viewCount))

ggplot(data = Performance) + geom_line(aes(x = date, y = maxview)) +
  geom_smooth(aes(x = date, y = maxview), se = FALSE) + ggtitle("Views by day")

```

# Comments Visualization
## Function : get_comments_by_id

```{r, eval=FALSE}
#Get Single Comment by Video_ID
get_comments_by_id <- function(x){
  commentData <- get_all_comments(video_id = x)
  print(commentData)
  }
Comments_1 <- get_comments_by_id("MJzALqFwxmo")
saveRDS(Comments_1, file= "Comments_example")
```

```{r}
Comments_1 <- readRDS(file="Comments_example")
```

## Function : WordCloud 

```{r, warning=FALSE}

print_word_cloud<- function(x= Comments_1$textOriginal, k=30){

comments_text = as.character(x)

comments_text = tibble(text = Reduce(c, comments_text)) %>%
  mutate(text = stri_trans_general(tolower(text), "Latin-ASCII"))
remove = c("you","the","que","and","your","muito","this","that","are","for","cara",
         "from","very","like","have","voce","man","one","nao","com","with","mais",
         "was","can","uma","but","ficou","meu","really","seu","would","sua","more",
         "it's","it","is","all","i'm","mas","como","just","make","what","esse","how",
         "por","favor","sempre","time","esta","every","para","i've","tem","will",
         "you're","essa","not","faz","pelo","than","about","acho","isso",
         "way","also","aqui","been","out","say","should","when","did","mesmo",
         "minha","next","cha","pra","sei","sure","too","das","fazer","made",
         "quando","ver","cada","here","need","ter","don't","este","has","tambem",
         "una","want","ate","can't","could","dia","fiquei","num","seus","tinha","vez",
         "ainda","any","dos","even","get","must","other","sem","vai","agora","desde",
         "dessa","fez","many","most","tao","then","tudo","vou","ficaria","foi","pela",
         "see","teu","those","were")
words = tibble(word = Reduce(c, stri_extract_all_words(comments_text$text))) %>%
  group_by(word) %>% count() %>% arrange(desc(n)) %>% filter(nchar(word) >= 3) %>%
  filter(n > k & word %in% remove == FALSE) 
 
set.seed(3)
wordcloud(words$word, words$n, random.order = FALSE, random.color = TRUE,
          rot.per = 0.3, colors = 1:nrow(words))
}
```

```{r, warning=FALSE}
# Default wordcloud is for the sample video in the NYT-Opinion section
# Why Ann Coulter Thinks President Trump Is 'Failing' | NYT - Opinion
print_word_cloud ()
```


```{r, warning=FALSE}
#WordCloud for Video Titles
print_word_cloud (NYT_Video$part1,3)
```


